% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=397249]
\definecolor[rulecolor][h=9cb770]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[youchao-xue]{Youchao Xue}

\thinrule

\subsubsection[personal-info]{PERSONAL INFO}

\placetable[none]{}
\starttable[|lp(0.45\textwidth)|rp(0.55\textwidth)|]
\HL
\NC DATE OF BIRTH: 14 Oct 1982
\NC PHONE: 781-332-2822
\NC\AR
\NC Home ADDRESS: 5 Junction Rd, North Reading , MA
\NC EMAIL: xueyouchao@gmail.com
\NC\AR
\NC Residency Status: greencard holder
\NC Blog: \useURL[url1][https://xueyouchao.github.io]\from[url1]
\NC\AR
\NC 
\NC \useURL[url2][http://youchaosdevelopment.blogspot.com/2009/03/few-videos-show-my-editor.html]\from[url2]
\NC\AR
\HL
\stoptable

\subsubsection[work-experience]{WORK EXPERIENCE}

\placetable[none]{}
\starttable[|lp(0.27\textwidth)|lp(0.73\textwidth)|]
\HL
\NC Apr 2012 \lettertilde{} Current
\NC {\bf Senior Security Engineer at Primeon Inc. Boston}
\NC\AR
\NC 
\NC Performing security code review and vulnerability assessment for top
500 corporations' web and mobile application; developing in-house
security analysis tool;
\NC\AR
\NC July 2009 \lettertilde{} Apr 2012
\NC {\bf 3D Graphics Developer at Weatherford International, Inverness
Team, UK}
\NC\AR
\NC 
\NC Developping and maintaining the 3D module of flagship software 5D, a
directional well planning and survey system that uses 3D visualization
for collision avoidance.
\NC\AR
\NC 
\NC {\bf Other key contributions:} In the project of drilling relief
well for Gulf of Mexico accident, I developed a small 3D application to
feed real time drilling data into 3D visualization viewer and provide a
quaternion based free roaming camera control, used by our senior
consultant Angus Jamieson and Houston Team to complete one of the most
challenging task in directional drilling area.
\NC\AR
\NC Aug 2005 \lettertilde{} Nov 2006
\NC {\bf Software Engineer at Huawei Technologies Co. Ltd., ShenZhen,
P.R. China}
\NC\AR
\NC 
\NC Joined several telecommunication projects, went through the full
life cycle of software development, including project planning,
requirements analysis, design, coding, debugging, unit testing, system
integration testing and release.
\NC\AR
\HL
\stoptable

\subsubsection[education]{Education}

\placetable[none]{}
\starttable[|lp(0.27\textwidth)|lp(0.73\textwidth)|]
\HL
\NC July 2007 \lettertilde{} May 2009
\NC {\bf University of Abertay Dundee,UK} - MSc Degree with Distinction
in Computer Games Technology
\NC\AR
\NC Sep 2001 \lettertilde{} July 2005
\NC {\bf Nanjing University of Aeronautics and Astronautics,China} -
Bachelor Degree in Information and Computational Science specialized
subject
\NC\AR
\HL
\stoptable

\subsubsection[technical-skills]{Technical Skills}

{\bf C/C++98 && C++11}\crlf
Deep understanding of C/C++ language including object oriented design,
c++ tempate programming, template metaprogramming, multithreading
programming, c++11 new memory model for concurrency programming and
lock-free programming.

{\bf Java & Objective C}\crlf
Performed Java source code review for several top 500 corporation Java
server side projects as well as Android and iOS mobile client side code
(or hybrid client using webview such as Cordova). Focused on web/mobile
security domain, familiar with major J2EE framework such as Struts2,
Spring framework; understanding of Java concurrency model, low level
multi-threading messaging library LMax Disruptor.

{\bf C\# & .net language}\crlf
Strong skill on c\# programming with experience on developing several
c\# based projects mixed with P/Invoke native funcations.Familiar with
c\# async programming and multithreading programming. Experience on
developing projects using c++/cli mixed with native c++ to bring .net UI
to native c++ code.

{\bf Other languages}\crlf
Strong interest on concurrency programming; although mainly focus on
c++11 concurrency programming, I also developed security analysis tool
using Golang based on its CSP model. Knowledge of different concurrency
approaches including SIMD, multithreading,functional programming, Actor,
CSP, GPGPU etc.

{\bf Developing Environment}\crlf
Emacs on Manjaro Linux and Visual Studio + Visual Assist X on Windows
Current write c++ project using
\useURL[url3][http://floooh.github.io/fips/getstarted.html][][Fips]\from[url3](cmake's
python binding) or
\useURL[url4][https://github.com/bkaradzic/GENie][][GENie]\from[url4](Lua
based premake), the tool helps to generate and compiles c++ code base
cross multiple compilers and cross different OS platforms including
Windows, Linux, OSX, iOS, Android, asm.js/Emscripten(superior web
browser solution), PNaCl etc. Familiar with various version control
including github, magit(github in emacs),bitbucket, Tortoise SVN,
Microsoft Team Foundation Server etc.

{\bf Library Used}\crlf
Strong ability of using STL, BOOST library, two years work experience of
Qt, experience of Ogre3D c++ engine, Nvidia Physx Engine, BGFX, ImGUI,
Raknet, NDK and many more.

\thinrule

\subsubsection[personal-side-projects]{Personal Side Projects}

\useURL[url5][http://youchaosdevelopment.blogspot.com/2009/02/world-of-champloo.html][][{\bf 3D
C++ Game: World of Champloo}]\from[url5]\crlf
Our team with 2 programmers and 3 artists developed this game with split
screen version(using XBOX controller) and networking version in less
than 2 months in 2008 using OGRE3D for 3D rendering engine, Physx for
Physics engine, OpenAL for game audio, CEGUI for ingame GUI, Raknet for
UDP networking communication.

\useURL[url6][http://youchaosdevelopment.blogspot.com/2009/03/few-videos-show-my-editor.html][][{\bf 3D
Game Editor for OGRE3D Engine with .net}]\from[url6]\crlf
My personal side project including the following features:\crlf
Visual studio style dockable .net window for rendering multiple 3D
scene, editor layout load/save from/to xml files\crlf
3D scene, model animations serialization/deserialization to/from XML
files\crlf
All the properties can be configured through unified .net property grid
etc.

\useURL[url7][https://xueyouchao.github.io/2017/02/26/Lock-Free-Ring-Queue-for-Multi-producer-and-Multi-consumer/][][{\bf Lock
Free Ring Queue for Multi-producer, Multi-consumer in
c++11}]\from[url7]\crlf
Demonstration of using C++11 to implement high efficient data structure
for lock-free programming.

\useURL[url8][https://xueyouchao.github.io/][][{\bf Personal Technical
Blog on Github}]\from[url8]\crlf
A techinical blog built with Markdown, Hexo on Github pages.

\thinrule

\subsubsection[certifications]{Certifications}

CISSP (Certified Information Systems Security Professional)

\thinrule

\subsubsection[resume-for-download]{Resume for download}

\useURL[url9][https://xueyouchao.github.io/about/resume.pdf][][PDF
version]\from[url9]\crlf
\useURL[url10][https://xueyouchao.github.io/about/resume.docx][][Word
version]\from[url10]\crlf
\useURL[url11][https://xueyouchao.github.io/about/resume.html][][HTML
version]\from[url11]\crlf
\useURL[url12][https://xueyouchao.github.io/about/resume.rtf][][RTF
version]\from[url12]

\stoptext
